### 2016-06-17 README.Rmd
minor readme updates

[![Travis-CI Build Status](https://travis-ci.org/cboettig/EML.svg?branch=master)](https://travis-ci.org/cboettig/EML)

@@

`EML` has not yet been released.  Please install from GitHub after installing the `devtools` package (from CRAN):

@@

```{r}
eml_validate(eml)
```

@@

```{r}
eml@dataset@ResourceGroup@pubDate <- new("pubDate", "2016")
```

>>>>

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)

@@

`EML` has not yet been released.  You can install the current development version from rOpenSci using:

```{r eval=FALSE}
install.packages("EML", repos = c("http://packages.ropensci.org", "https://cran.rstudio.com"))
```

or install directly from GitHub (after installing the `devtools` package from CRAN):

@@

```{r, message=TRUE}
# An EML document with no validation errors
eml_validate(eml)

# An EML document with validation errors
invalid_eml <- system.file("tests/testthat/", "example-eml-invalid.xml", package = "EML")

eml_validate(invalid_eml)
```

@@

```{r}
eml@dataset@pubDate <- new("pubDate", "2016")
```
